### 2019-02-25 manuscript/results.tex

We found that when considered alone, ploidy and breeding system each showed significant associations with net diversification differences.
When considered together, however, the effect of breeding system dominated the effect of ploidy, although hidden factors played an important role as well.

For ploidy alone (D/P model), we found a larger net diversification rate for diploids than for polyploids, in agreement with \citet{mayrose_2011, mayrose_2015}.
This result holds with (\cref{figure:netdivall}A) or without (\cref{figure:netdivnodip}A) the diploidization parameter, though including diploidization shifts the net diversification rate of polyploids to be non-negative.
Incorporating a hidden state, however, removes the clear separation in diversification between diploids and polyploids (D/P+A/B model; \cref{figure:netdivall}B, \cref{figure:netdivnodip}B).
Thus, differences in net diversification are better explained by an unknown factor than by ploidy.
Statistical model comparisons show very strong support for including the hidden state and strong support for including diploidization (\cref{table:bayesfactors}).
% E: I removed the description of relative extinction results.  We don't discuss it for other models or show it in the main text, and I never really know what to make of that compound parameter.  But it's good that it's in the supp info.

>>>>

We found that when considered alone, ploidy and breeding system each showed significant associations with net diversification differences. %B: check and deleteme: I think this should have "states" added, so "...ploidy and breeding system states showed..."
When considered together, however, the effect of breeding system dominated the effect of ploidy, although hidden factors played an important role as well. %B: same here.

%B: The "For X (states model), we found" template doesn't sound quite right to me. Maybe, "Fitting" or "Considering" or "When" (as in second portion with hidden-state model. In latter case, possibly (1) When considering X alone..., (2) Addition of... / Incorporating a hidden state...
%
For ploidy alone (D/P model), we found a greater net diversification rate for diploids than for polyploids, in agreement with \citep{mayrose_2011, mayrose_2015}.
This result holds with (\cref{figure:netdivall}A) or without (\cref{figure:netdivnodip}A) the diploidization parameter, though including diploidization shifts the net diversification rate of polyploids to be non-negative.
Incorporating a hidden state, however, removes the clear separation in diversification between diploids and polyploids (D/P+A/B model; \cref{figure:netdivall}B, \cref{figure:netdivnodip}B).
Thus, differences in net diversification are better explained by an unknown factor than by ploidy.
Statistical model comparisons show very strong support for including the hidden state and strong support for including diploidization (\cref{table:bayesfactors}).
% E: I removed the description of relative extinction results.  We don't discuss it for other models or show it in the main text, and I never really know what to make of that compound parameter.  But it's good that it's in the supp info.
